Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-08-02 Paper/main.tex
Update graphs

\begin{table}[H]
\caption{Determinants of overconfidence}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use the following statistic to measure overconfidence: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

%#include
\begin{table}[H]
\caption{Compliance rate}
\label{Table_compliance}
\begin{center}
\scriptsize{\input{./Tables/Compliance.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
The number of cases assigned to the 3 different groups is very similar, and is close to 7 per day on average. The compliance with treatment rate is similar for both treatments and in the range of 75\%.
\textit{Do file: } \texttt{table\_compliance.do}
\end{table}

%#include
\begin{table}[H]
\caption{Balance table conditional on compliance}
\label{Table_compliance}
\begin{center}
\scriptsize{\input{./Tables/Balance.tex}}
\end{center}
 \footnotesize
\textit{Notes: Balance table on some basic and strategic variables, conditional on compliance to treatment. Practically none of them significantly differ in mean across treatment groups, at the 5\% level.} 
\textit{Do file: } \texttt{balance.do}
\end{table}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
%    \begin{subfigure}{\textwidth}
%        \caption{update in beliefs in duration}
%        \centering
%        \includegraphics[width=\textwidth]{updatebeleif_duration.pdf}
%    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount}
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount_1.pdf}
    \end{subfigure}

        \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Scale Up)}
        \centering
        \includegraphics[width=\textwidth, height=0.25\textheight]{updatebeleif_amount_2.pdf}
    \end{subfigure}

    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph only considers observations that falls between 0 and 1; and the \% of the observations that fall in that range are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Pilot) }
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount_total_1.pdf}
    \end{subfigure}

        \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Scale Up) }
        \centering
        \includegraphics[width=\textwidth, height=0.25\textheight]{updatebeleif_amount_total_2.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph considers all observations but some outliers; the \% of the observations considered are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs\_total.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Out of sample fit for duration predictions}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of duration predictions and outcomes }
        {\footnotesize \textit{RScript: }  \texttt{covariate_plots.R}}
\end{figure}

\begin{figure}[H]
    \caption{Out of sample fit for compensation predictions}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes.}
        {\footnotesize \textit{RScript: }  \texttt{covariate_plots.R}}
\end{figure}

>>>>

\begin{table}[H]
\caption{Determinants of updating}
\label{Table_determinants_updating}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use the following statistic to measure updating: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

\begin{table}[H]
    \caption{Compliance Rate}
    \label{Table_compliance}
    \begin{subtable}{1\textwidth}
      \centering
        \caption{Pilot}
        \scriptsize{\input{./Tables/Compliance.tex}}
    \end{subtable}%

    \bigskip
    \begin{subtable}{1\textwidth}
      \centering
        \caption{Scale Up}
        \scriptsize{\input{./Tables/Compliance_2.tex}}
    \end{subtable}
           \footnotesize
           \\
           \\
           \\
  \textit{Notes:} 
    Compliance Rate for each experiment, both for treatment and survey. Note that randomization is done at the casefile level, for the pilot, and at the day-subcourt level, for the scale-up. Both tables case numbers for the Assignment column, and rates for Compliance.
    \textit{Scripts: } \texttt{table\_compliance.do, balance\_compliance.R}
\end{table}

\begin{table}[H]
    \caption{Balance Table conditional on compliance}
    \label{Table_balance}
    \begin{subtable}{1\textwidth}
      \centering
        \caption{Pilot}
        \scriptsize{\input{./Tables/Balance.tex}}
    \end{subtable}%

    \bigskip
    \begin{subtable}{1\textwidth}
      \centering
        \caption{Scale Up}
        \scriptsize{\input{./Tables/balance_2.tex}}
    \end{subtable}
           \footnotesize 
           \\
           \\
           \\
  \textit{Notes:} 
    Balance table on some basic and strategic variables, conditional on compliance to treatment. Practically none of them significantly differ in mean across groups, at the 5\% level.
    \textit{Scripts: } \texttt{balance.do, balance\_compliance.R}
\end{table}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
     \begin{center}
        \includegraphics[width=0.9\textwidth]{updatebeleif_amount.pdf}
        \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph only considers observations that falls between 0 and 1; and the \% of the observations that fall in that range are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
     \begin{center}
        \includegraphics[width=0.9\textwidth]{updatebeleif_amount_total.pdf}
        \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph considers all observations but some outliers; the \% of the observations considered are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs\_total.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Out of sample fit for duration predictions}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of duration predictions and outcomes }
        {\footnotesize \textit{RScript: }  \texttt{covariate\_plots.R}}
\end{figure}

\begin{figure}[H]
    \caption{Out of sample fit for compensation predictions}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes.}
        {\footnotesize \textit{RScript: }  \texttt{covariate\_plots.R}}
\end{figure}
